Resolving the measurement uncertainty paradox in ecological management

### 2018-11-22 manuscripts/manuscript.Rmd
double-escape in latex in captions

```{r econ, fig.width=7, fig.height=3.5, fig.cap="Expected net present value of the fishery across strategies under increasing levels of measurement error $\\sigma_m$. Net present value is the sum of all future harvests discounted over time and averaged across 100 replicates simulations under each strategy, assuming discount factor $\gamma = 0.95$, as shown in Figure \\ref{sims}. The value under constant escapement (CE) is optimal when measurements are perfect but decreases rapidly with increasing measurement error. The more cautious TAC is not economically optimal but largely unimpacted by increasing error, while POMDP attains consistently high economic yield despite the increasing uncertainty. \\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "MSY") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

>>>>

```{r econ, fig.width=7, fig.height=3.5, fig.cap="Expected net present value of the fishery across strategies under increasing levels of measurement error $\\sigma_m$. Net present value is the sum of all future harvests discounted over time and averaged across 100 replicates simulations under each strategy, assuming discount factor $\\gamma = 0.95$, as shown in Figure \\ref{sims}. The value under constant escapement (CE) is optimal when measurements are perfect but decreases rapidly with increasing measurement error. The more cautious TAC is not economically optimal but largely unimpacted by increasing error, while POMDP attains consistently high economic yield despite the increasing uncertainty. \\label{econ}"}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g == "0.15", method != "MSY") %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%
